---
title: "Custom closures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Custom closures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
references:
- id: wickham2014
  title: Advanced R
  author:
  - family: Wickham
    given: Hadley
  publisher: Chapman and Hall/CRC
  type: book
  issued:
    year: 2014
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SimSurvey)
```


## Built-in closures

The **`SimSurvey`** package makes frequent use of "closures", which are functions that contain data and return functions [@wickham2014], to control how the simulations are strucured. There are various closures built into the package and the data supplied to these closures tend to be parameter inputs and the closures return functions that require inputs such as ages and/or years. This was done to avoid the repeated specifications of key arguments, such as ages and years. Moreover, this approach provides an option for advanced R users to inspect and modify the closures implemented in the package to supply custom closures with alternate equations. For instance, the `sim_logistic` closure was created to control the shape of survey catchability and it requires parameter inputs that control the shape of the logistic curve and it returns a function that requires a vector of ages.

```{r}

sim_logistic <- function(k = 2, x0 = 3, plot = FALSE) {
  function(x = NULL) {
    y <- 1 / (1 + exp(-k * (x - x0)))
    if (plot) plot(x, y, type = "b")
    y
  }
}

```

Such that when this closure is run, the object returned is a function.

```{r}
ages <- 1:20
logistic_fun <- sim_logistic(k = 1, x0 = 5)
logistic_curve <- logistic_fun(ages)
plot(x = ages, y = logistic_curve, xlab = "Age", ylab = "Catchability", type = "l")
```

Notice that some simple plotting code has been included inside the `sim_logistic` closure, as it is with the other closures included with **`SimSurvey`**, such that when `plot = TRUE` a plot is automatically generated. This is useful for visual explorations of parameter settings.

When these closures are supplied to the core functions of **`SimSurvey`**, the argument ends up being a function and this function is used internally to control various aspects of the simulation, such as the shape of survey catchability. The internal inputs to these functions (e.g. ages and years) can therefore be dynamic.

```{r, eval = FALSE}

set.seed(438)
sim <- sim_abundance() %>% 
  sim_distribution() %>% 
  sim_survey(n_sims = 5, q = sim_logistic(k = 1, x0 = 5))

```



## Custom closures

Users are not restricted to the limited number of parametric relationships captured inside the closures built into the **`SimSurvey`** package. The code can be copied and modified to impose different relationships. For instance, the `sim_logistic` closure can be modified to make a `sim_gaussian` closure for use in the `sim_survey` function to impose dome-shaped survey catchability.


```{r}

sim_gaussian <- function(a = 1, b = 10, c = 5, plot = FALSE) {
  function(x = NULL) {
    y <- a * exp(-((x - b) ^ 2) / (2 * c ^ 2))
    if (plot) plot(x, y, type = "b")
    y
  }
}

gaussian_fun <- sim_gaussian(b = 15, c = 5)
gaussian_curve <- gaussian_fun(ages)
plot(x = ages, y = gaussian_curve, xlab = "Age", ylab = "Catchability", type = "l")

```


And this closure can be used in lieu of `sim_logistic`.

```{r, eval = FALSE}

set.seed(438)
sim <- sim_abundance() %>% 
  sim_distribution() %>% 
  sim_survey(n_sims = 5, q = sim_gaussian(b = 15, c = 5))

```

## References



